\large \textbf{Title:} Computational models reveal how cleaner fish adjust decisions in a biological market

### 2022-08-15 manuscript_BE/manuscript_BE.Rmd
Further changes to include PAA in the analysis. Dealing with convergence problems

---
title: | 
  \large \textbf{Title:} Computational models reveal how cleaner fish adjust decisions in a biological market
subtitle: |
  \normalsize \textbf{Abbreviated title:} Cleaner fish cognitive mechanisms in a biological market
# date: "`r format(Sys.time(), '%B %d, %Y')`"
# author: 
#   - name: Andrés E. Quiñones 
#     email: andresqp@gmail.com
#     affiliation: a
#     corresponding: andresqp@gmail.com 
#     #, Rue Emile-Argand 11, CH-2000, Neuchatel, Switzerland. +41 32 718 31 24
#   - name: Zegni Triki
#     affiliation: a
#     affiliation: b
#   - name: Redouan Bshary
#     affiliation: a
# address:
#   - code: a
#     address: Institute of Biology, University of Neuchatel, Neuchatel, Switzerland
#   - code: b
#     address: Department of Zoology, Stockholm University, Stockholm, Sweden
output:
   pdf_document:
    keep_tex: true
    latex_engine: xelatex
    template: template.latex
fig_caption: yes
fontsize: 12pt
keep_tex: yes
bibliography: Cleanerlearning.bib
style: M:\Zotero\styles\behavioral-ecology.csl
spacing: double
abstract: |
  While it is generally straightforward to quantify individual performance in cognitive experiments, identifying the underlying cognitive processes remains a major challenge. Often, different mechanistic underpinnings yield similar performances, and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation. Alternatively, when the different mechanisms interact with environmental conditions, variation in performance across environments might allow to statistically infer the mechanism responsible. We illustrate this point by fitting computational models to experimental data on performance by wild-caught cleaner fish *Labroides dimidiatus* in an ephemeral reward task, as well as cleaner and client fish densities from the locations of capture. Using Bayesian statistics to fit the model parameters to performance data revealed that cleaner fish most likely estimate future consequences of an action, while it appears unlikely that the removal of the ephemeral reward acts as psychological punishment (negative reinforcement). Incorporating future consequences also yields performances that can be considered the result of locally optimal decision-rules, in contrast to the negative reinforcement mechanism. We argue that the combination of computational models with data is a powerful tool to infer the mechanistic underpinnings of cognitive performance. 
lay_summary: |
  Cleaner fish eat ectoparasites off other fishes, so-called clients. It regularly happens that two clients seek a cleaner's service simulatenously. Cleaners benefit from prioritising clients unwilling to wait, so they can feed on those willing to wait. To make the right choice, cleaners must somehow “look” into the future to anticipate consequences of current choices. By combining a learning model with data, we show that cleaners estimate the long-term value of their actions rather than using simpler heuristics. Estimating long-term value is a mechanism involved in human foresight.
header-includes: |
  ```{=latex}
  \usepackage{float}
  \usepackage{graphicx}
  \usepackage{booktabs}
  \linespread{2}
  \usepackage{lineno}
  \linenumbers
  \usepackage{setspace}\doublespacing
  \newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  \providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
  ```
editor_options:
  markdown:
    wrap: 80
---

@@

source(here("analysisMCMC.R"))
first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
          gam.both.post,gam.gam.post,nrew.nrew.post,
          labels=c('a','c','d'))
second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
          nrew.both.post,panel.rsqr.all,rel_heights = c(1,2),
          labels = c('b','e'))
plot_grid(ncol = 2,first.col,second.col)

@@

```{r scaConst, fig.cap='Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only). We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval. On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.',fig.pos = 'H', out.extra = "",out.width='95%',fig.height=5}

@@

@@

```{r diagnosticsfull, fig.cap='MCMC convergence diagnostics for the full model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.',out.width='100%',fig.height=5,cache=FALSE,message=FALSE}

@@

```{r diaggam,fig.cap='MCMC convergence diagnostics for the chaining model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor ',echo=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
longMCMCdata2<-melt(MCMCdata2,id.vars = c("iteration","seed"),
                    variable.name = "parameter",
                    measure.vars = c("gamma","scaleConst"))

parlab<-list(`gamma` =expression(gamma),
          `scaleConst`="Scaling constant")

traces.gam<-ggplot(longMCMCdata2,aes(x=iteration,y=value,colour=as.factor(seed)))+
  geom_line()+
  scale_color_manual(values = multDiscrPallet)+
  labs(color="Chain")+
  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
             labeller = function(variable,value){
  return(parlab[value])})+
  theme_classic()+
  theme(legend.position = 'top')

@@

```{r diagNeg,fig.cap='MCMC convergence diagnostics for the penalty model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor',out.width='100%',fig.height=5,cache=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
longMCMCdata3<-melt(MCMCdata3,id.vars = c("iteration","seed"),
                    variable.name = "parameter",
                    measure.vars = c("negReward","scaleConst"))

parlab<-list(`negReward` =expression(eta),
          `scaleConst`="Scaling constant")

traces.neg<-ggplot(longMCMCdata3,aes(x=iteration,y=value,colour=as.factor(seed)))+
  geom_line()+
  scale_color_manual(values = multDiscrPallet)+
  labs(color="Chain")+
  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
             labeller = function(variable,value){
  return(parlab[value])})+
  theme_classic()+
  theme(legend.position = 'top')

@@

>>>>

---
title: |
  \large \textbf{Title:} Computational models reveal how cleaner fish adjust decisions in a biological market
subtitle: |
  \normalsize \textbf{Abbreviated title:} Cleaner fish cognitive mechanisms in a biological market
output:
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    template: template.latex
  word_document: default
fig_caption: yes
fontsize: 12pt
keep_tex: yes
bibliography: Cleanerlearning.bib
style: "M:\\Zotero\\styles\\behavioral-ecology.csl"
spacing: double
abstract: |
  While it is generally straightforward to quantify individual performance
  in cognitive experiments, identifying the underlying cognitive processes remains
  a major challenge. Often, different mechanistic underpinnings yield similar performances,
  and Lloyd Morgan’s cannon warrants acceptance of the simpler explanation. Alternatively,
  when the different mechanisms interact with environmental conditions, variation
  in performance across environments might allow to statistically infer the mechanism
  responsible. We illustrate this point by fitting computational models to experimental
  data on performance by wild-caught cleaner fish *Labroides dimidiatus* in an ephemeral
  reward task, as well as cleaner and client fish densities from the locations of
  capture. Using Bayesian statistics to fit the model parameters to performance data
  revealed that cleaner fish most likely estimate future consequences of an action,
  while it appears unlikely that the removal of the ephemeral reward acts as psychological
  punishment (negative reinforcement). Incorporating future consequences also yields
  performances that can be considered the result of locally optimal decision-rules,
  in contrast to the negative reinforcement mechanism. We argue that the combination
  of computational models with data is a powerful tool to infer the mechanistic underpinnings
  of cognitive performance.
lay_summary:  |
  Cleaner fish eat ectoparasites off other fishes, so-called clients.
  It regularly happens that two clients seek a cleaner's service simulatenously. Cleaners
  benefit from prioritising clients unwilling to wait, so they can feed on those willing
  to wait. To make the right choice, cleaners must somehow “look” into the future
  to anticipate consequences of current choices. By combining a learning model with
  data, we show that cleaners estimate the long-term value of their actions rather
  than using simpler heuristics. Estimating long-term value is a mechanism involved
  in human foresight.
header-includes: |
  ```{=latex}
    \usepackage{float}
    \usepackage{booktabs}
    \newcommand{\beginsupplement}{ \setcounter{table}{0}             \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  ```
editor_options:
  markdown:
    wrap: 80
---

@@

source(here("analysisMCMC.R"))

ggarrange(allGammapost.plot,alletapost.plot,common.legend = TRUE)
# first.col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
#           gam.both.post.FAA,gam.gam.post.FAA,nrew.nrew.post.FAA,
#           labels=c('a','c','d'))
# second.col<-plot_grid(nrow = 2,align = "v",byrow = TRUE,
#           nrew.both.post.FAA,panel.rsqr.all,rel_heights = c(1,2),
#           labels = c('b','e'))
# plot_grid(ncol = 2,first.col,second.col)

@@

```{r scaConstFAA, fig.cap='Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only). We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval. On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.',fig.pos = 'H', out.extra = "",out.width='95%',fig.height=5}

@@

```{r scaConstPAA, fig.cap='Posterior distributions for scaling constant for the three models (Full model, chaining only and penalty only). We show the kernel density estimates, below the mode (black dot) and the 65\\% (light blue shade) and 95\\% (grey shade)  highest posterior density interval. On the top, panel a shows the posterior distribution from the full model; panel b from the model with only chaining; and panel c from a model with only penalty.',fig.pos = 'H', out.extra = "",out.width='95%',fig.height=5}

sca.both.post.PAA<-ggplot(data=MCMCdata4,aes(x=scaleConst)) + 
  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.4$scaleConst))),
               point_interval = mode_hdi, .width = c(.66, .95),
               point_size=3,show.legend=FALSE) + 
  labs(title=labelsPlot.Scen[1],x="",y="")+
  theme_classic()+
  scale_fill_manual(values=c("gray85","skyblue","gray85"))
sca.gam.post.PAA<-ggplot(data=MCMCdata5,aes(x=scaleConst)) + 
  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.5$scaleConst))),
               point_interval = mode_hdi, 
               .width = c(.66, .95),point_size=3,
               show.legend=FALSE)+theme_classic()+
  scale_fill_manual(values=c("gray85","skyblue","gray85"))+
  labs(title=labelsPlot.Scen[2],x="",y="")
sca.nRew.post.PAA<-ggplot(data=MCMCdata6,aes(x=scaleConst)) +
  stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.6$scaleConst))),
               point_interval = mode_hdi, .width = c(.66, .95),
               point_size=3,
               show.legend=FALSE) +
  scale_fill_manual(values=c("skyblue","gray85"))+
  labs(title=labelsPlot.Scen[3],x="",y="")+
  theme_classic()
ggarrange(sca.both.post.PAA,sca.gam.post.PAA,
          sca.nRew.post.PAA,
          labels=c('a','b','c'),common.legend = F)

@@

```{r diagnosticsfullFAA, fig.cap='MCMC convergence diagnostics for the full model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.',out.width='100%',fig.height=5,cache=FALSE,message=FALSE}

@@

```{r diaggamFAA,fig.cap='MCMC convergence diagnostics for the chaining model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor ',echo=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
longMCMCdata2<-melt(MCMCdata2,id.vars = c("iteration","seed"),
                    variable.name = "parameter",
                    measure.vars = c("gamma","scaleConst"))

longMCMCdata2[,parameter:=factor(parameter,labels=c("gamma","'Scaling constant'"))]

traces.gam<-ggplot(longMCMCdata2,aes(x=iteration,y=value,colour=as.factor(seed)))+
  geom_line()+
  scale_color_manual(values = multDiscrPallet)+
  labs(color="Chain")+
  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
             labeller = label_parsed)+
  theme_classic()+
  theme(legend.position = 'top')

@@

```{r diagNegFAA,fig.cap='MCMC convergence diagnostics for the penalty model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor',out.width='100%',fig.height=5,cache=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
longMCMCdata3<-melt(MCMCdata3,id.vars = c("iteration","seed"),
                    variable.name = "parameter",
                    measure.vars = c("negReward","scaleConst"))

longMCMCdata3[,parameter:=factor(parameter,labels=c("eta","'Scaling constant'"))]

traces.neg<-ggplot(longMCMCdata3,aes(x=iteration,y=value,colour=as.factor(seed)))+
  geom_line()+
  scale_color_manual(values = multDiscrPallet)+
  labs(color="Chain")+
  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
             labeller = label_parsed)+
  theme_classic()+
  theme(legend.position = 'top')

@@

```{r diagnosticsfullPAA, fig.cap='MCMC convergence diagnostics for the full model. On the left trace-plots, fig.height=5, message=FALSE, cache=FALSE, on the right changes along the chain of the Gelman and Rubin shrink factor.',out.width='100%'}

longMCMCdata4<-melt(MCMCdata4,id.vars = c("iteration","seed"),
                    variable.name = "parameter",
                    measure.vars = c("gamma","negReward","scaleConst"))

traces.full.PAA<-ggplot(longMCMCdata4,aes(x=iteration,y=value,colour=as.factor(seed)))+
  geom_line()+
  scale_color_manual(values = multDiscrPallet)+
  labs(color="Chain")+
  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
             labeller = function(variable,value){
  return(parlab[value])})+
  theme_classic()+
  theme(legend.position = 'top')

gel.full<-as.data.table(gelman.diag(mcmcList.4)$psrf)
gel.full[,parameter:=c("gamma","negReward","scalConst")]

pdf(file = NULL)
gp.dat<-gelman.plot(mcmcList.4)
rubbish <- dev.off()

gp.dat.frame.PAA <- data.table(rbind(as.data.frame(gp.dat[["shrink"]][,,1]),
                          as.data.frame(gp.dat[["shrink"]][,,2])),
                q=rep(dimnames(gp.dat[["shrink"]])[[3]], each=nrow(gp.dat[["shrink"]][,,1])),
                last.iter=rep(gp.dat[["last.iter"]], length(gp.dat)))

gelman.full.PAA<-ggplot(melt(gp.dat.frame.PAA, c("q","last.iter"), value.name="shrink_factor"),
       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
  geom_line() +
  facet_grid(rows = vars(variable)) +
  labs(x="Last Iteration in Chain", y="Shrink Factor",
       colour="Quantile", linetype="Quantile") +
  scale_linetype_manual(values=c(2,1))+
  theme_classic()+
  theme(legend.position = 'top',strip.text.y  = element_blank())

ggarrange(traces.full.PAA,gelman.full.PAA)

```{r diaggamPAA,fig.cap='MCMC convergence diagnostics for the chaining model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor ',echo=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
longMCMCdata5<-melt(MCMCdata5,id.vars = c("iteration","seed"),
                    variable.name = "parameter",
                    measure.vars = c("gamma","scaleConst"))

longMCMCdata5[,parameter:=factor(parameter,labels = c("gamma","'Scaling constant'"))]

traces.gam.PAA<-ggplot(longMCMCdata5,aes(x=iteration,y=value,colour=as.factor(seed)))+
  geom_line()+
  scale_color_manual(values = multDiscrPallet)+
  labs(color="Chain")+
  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
             labeller = label_parsed)+
  theme_classic()+
  theme(legend.position = 'top')

gel.gam<-as.data.table(gelman.diag(mcmcList.5)$psrf)
gel.gam[,parameter:=c("gamma","scalConst")]

pdf(file = NULL)
gp.dat.gam<-gelman.plot(mcmcList.5)
rubbish <- dev.off()

gp.dat.frame.gam.PAA <- data.table(rbind(as.data.frame(gp.dat.gam[["shrink"]][,,1]),
                          as.data.frame(gp.dat.gam[["shrink"]][,,2])),
                q=rep(dimnames(gp.dat.gam[["shrink"]])[[3]], each=nrow(gp.dat.gam[["shrink"]][,,1])),
                last.iter=rep(gp.dat.gam[["last.iter"]], length(gp.dat.gam)))

gelman.gam.PAA<-ggplot(melt(gp.dat.frame.gam.PAA, c("q","last.iter"), value.name="shrink_factor"),
       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
  geom_line() +
  facet_grid(rows = vars(variable)) +
  labs(x="Last Iteration in Chain", y="Shrink Factor",
       colour="Quantile", linetype="Quantile") +
  scale_linetype_manual(values=c(2,1))+
  theme_classic()+
  theme(legend.position = 'top',strip.text.y = element_blank())

ggarrange(traces.gam.PAA,gelman.gam.PAA)
```

```{r diagNegPAA,fig.cap='MCMC convergence diagnostics for the penalty model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor',out.width='100%',fig.height=5,cache=FALSE,message=FALSE,out.width='100%',fig.height=5,cache=FALSE,message=FALSE}
longMCMCdata6<-melt(MCMCdata6,id.vars = c("iteration","seed"),
                    variable.name = "parameter",
                    measure.vars = c("negReward","scaleConst"))

longMCMCdata6[,parameter:=factor(parameter,labels = c("eta","'Scaling constant'"))]

traces.neg.PAA<-ggplot(longMCMCdata6,aes(x=iteration,y=value,colour=as.factor(seed)))+
  geom_line()+
  scale_color_manual(values = multDiscrPallet)+
  labs(color="Chain")+
  facet_grid(rows=vars(parameter),scales = "free",switch = "y",
             labeller = label_parsed)+
  theme_classic()+
  theme(legend.position = 'top')

pdf(file = NULL)
gp.dat.neg<-gelman.plot(mcmcList.6)
rubbish <- dev.off()

gp.dat.frame.neg.PAA <- data.table(rbind(as.data.frame(gp.dat.neg[["shrink"]][,,1]),
                          as.data.frame(gp.dat.neg[["shrink"]][,,2])),
                q=rep(dimnames(gp.dat.neg[["shrink"]])[[3]], each=nrow(gp.dat.neg[["shrink"]][,,1])),
                last.iter=rep(gp.dat.neg[["last.iter"]], length(gp.dat.neg)))

gelman.neg.PAA<-ggplot(melt(gp.dat.frame.neg.PAA, c("q","last.iter"), value.name="shrink_factor"),
       aes(last.iter, shrink_factor, colour=q, linetype=q)) +
  geom_hline(yintercept=1, colour="grey30", lwd=0.2) +
  geom_line() +
  facet_grid(rows = vars(variable)) +
  labs(x="Last Iteration in Chain", y="Shrink Factor",
       colour="Quantile", linetype="Quantile") +
  scale_linetype_manual(values=c(2,1))+
  theme_classic()+
  theme(legend.position = 'top',strip.text.y = element_blank())

ggarrange(traces.neg.PAA,gelman.neg.PAA)
```

### 2022-08-15 manuscript_BE/manuscript_BE.tex
Further changes to include PAA in the analysis. Dealing with convergence problems

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{float}
\usepackage{graphicx}
\usepackage{booktabs}
\linespread{2}
\usepackage{lineno}
\linenumbers
\usepackage{setspace}\doublespacing
\newcommand{\beginsupplement}{ \setcounter{table}{0}     \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagnosticsfull-1} \caption{MCMC convergence diagnostics for the full model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfull}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diaggam-1} \caption{MCMC convergence diagnostics for the chaining model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor }\label{fig:diaggam}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagNeg-1} \caption{MCMC convergence diagnostics for the penalty model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor}\label{fig:diagNeg}
\end{figure}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
  \usepackage{float}
  \usepackage{booktabs}
  \newcommand{\beginsupplement}{ \setcounter{table}{0}             \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagnosticsfullFAA-1} \caption{MCMC convergence diagnostics for the full model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfullFAA}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diaggamFAA-1} \caption{MCMC convergence diagnostics for the chaining model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor }\label{fig:diaggamFAA}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagNegFAA-1} \caption{MCMC convergence diagnostics for the penalty model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor}\label{fig:diagNegFAA}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagnosticsfullPAA-1} \caption{MCMC convergence diagnostics for the full model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor.}\label{fig:diagnosticsfullPAA}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diaggamPAA-1} \caption{MCMC convergence diagnostics for the chaining model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor }\label{fig:diaggamPAA}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_BE_files/figure-latex/diagNegPAA-1} \caption{MCMC convergence diagnostics for the penalty model. On the left trace-plots, on the right changes along the chain of the Gelman and Rubin shrink factor}\label{fig:diagNegPAA}
\end{figure}
